---
title: "Data Cleaning per la Ricerca Clinica"
subtitle: "Clinical Research Academy"
author: "[CorradoLanera](www.CorradoLanera.it)"
date: "2021-10-13 (last update: `r Sys.Date()`)"
output: 
  xaringan::moon_reader:
    seal: false  # no title slide! Do It Yourself
    nature:
      highlightStyle: github
      highlightLines: true
    css: xaringan-themer.css
---
name: title
class: center, middle
background-image: url(http://bit.ly/arm-greens)
background-size: cover

# Data Cleaning per la Ricerca Clinica
<img src="http://bit.ly/arm-greens" width="150px"/>

### Con esempi in R

.large[.white[
  Corrado Lanera | Clinical Research Academy | 13 Oct 2021
]]


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.retina = 3,
  warning = FALSE,
  message = FALSE,
  comment = ""
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
red <- "#f34213"
purple <- "#3e2f5b"
orange <- "#ff8811"
green <- "#136f63"
white <- "#FFFFFF"

pastel_orange <- "#F97B64"
blu_gray <- "#1F4257"

style_duo_accent(
    primary_color = pastel_orange,
    secondary_color = blu_gray,
    colors = c(
        red = red,
        purple = purple,
        orange = orange,
        green = green,
        white = white,
        pastel_orange = pastel_orange,
        blu_gray = blu_gray
    )
)
```

```{r xaringanExtra, echo=FALSE}
xaringanExtra::use_xaringan_extra(c(
  "tileview",
  "animate_css",
  "tachyons",
  "editable",
  "panelset",
  "webcam",
  "clipboard",
  "freezeframe",
  "share_again"
))

xaringanExtra::use_logo(
  image_url = "https://raw.githubusercontent.com/rstudio/hex-stickers/master/PNG/xaringan.png",
  link_url = "http://slides.yihui.name/xaringan",
  position = xaringanExtra::css_position(top = "1em", right = "1em")
)

```

```{r countdown, echo = FALSE}
library(countdown)
# countdown(minutes = 0, seconds = 15)
```

---
class: inverse, middle, center

# let's start!
---

name: intro



# Introduce yourself!

> My name is Corrado and I am a Post-doc researcher at the Univerity of Padova at the Unit of Biostatistics, Epidemiology, and Public Health within the department of Cardiac, Thoracic, Vascular Sciences, and Public Health. I am an RStudio Instructor in the Tidyverse, and I love R. I 
live a little arround Italy and Europe, from Udine (my family home), Padova (my Job office), Paris (my spouse work), and any other possible place along the way.

**foo**


---
name: findmeat


# Find me at...
All the details...




---

[goto somewhere](#somewhere) -> hop to somewhere

???

click **goto**


---
name: somewhere
class: center, middle

# This is really something!

.left[words]
.center[words]
.right[words]


---
name: images
class: center, middle

Hello ![Image of Momtocat](http://bit.ly/momtocat)


---
.pull-left[
![Image of Momtocat](http://bit.ly/momtocat)
]
.pull-right[
![Image of Poptocat](http://bit.ly/poptocat)
]


---
name: code

```{r, eval=FALSE, highlight.output = TRUE}
foo
bar  #<<
baz
```

```{r, highlight.output = TRUE}
1+1
```

```{r, highlight.output = c(1, 3)}
1+1
2+2
3+3
```

---

.pull-left[
```{r plot-first, echo = FALSE}
ggplot2::quickplot(
    mtcars[[1]],  #<<
    mtcars[[2]]
)
```
]
.pull-right[
```{r ref.label = 'plot-first', eval = FALSE}
```
]


---
background-image: url(http://bit.ly/arm-greens)

---
background-image: url(http://bit.ly/arm-greens)
background-size: cover

---
background-image: url(http://bit.ly/arm-greens)
background-size: contain

---

```{r out.width = '50%'}
# url
knitr::include_graphics("http://bit.ly/arm-greens")
```
